Smart Representations: {R}ationality and Evolution in a Richer Environment

### 2016-06-30 paper/rev1_paperBlinded.tex
paper revision micha final edits

If agents deal with a rich and variable environment, they have to face many different choice
situations.  Standard evolutionary game models frequently simplify reality in at least two
ways. Firstly, the environment is represented as a fixed \emph{stage game}; secondly, the focus
of evolutionary selection is behavior for that stage game alone. In contrast, some argue for
studying the evolutionary competition of general \emph{choice mechanisms} in a rich and
variable environment
\citep[e.g.,][]{FawcettHamblin2013:Exposing-the-be,McNamara2013:Towards-a-Riche,HammStev12}. In
response to this and adding to recent like-minded approaches, this paper introduces a general
\emph{meta-game} model that conservatively extends the scope of evolutionary game theory to deal with
evolutionary selection of choice mechanisms in variable environments \citep[see also][]{Harley1981:Learning-the-Ev,ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o,OConnor2016:Evolving-to-Gen,RayoBecker07,Zollman2008,SkyrmsZollman10,BednarPage07}.\footnote{In particular, similar ideas appear in \citep{RayoBecker07,Zollman2008,BednarPage07}. \citep{BednarPage07} use a multi-game framework, composed of a fixed selection of six possible games, to study the emergence of different cultural behaviors, and model agents as finite-state automata playing games from the fixed selection. \citep{Zollman2008} explains seemingly ``irrational'' fair behavior in social dilemmas (like the Ultimatum game) by means of a model where agents have to play the Ultimatum game together with the Nash bargaining game, but they are constrained to choose the same strategy for both games. Finally, \citep{RayoBecker07} consider, in a more decision-theoretic setting, what subjective utility function a cognitively limited agent should be endowed with in order to maximize her evolutionary fitness. Our framework can then be viewed as a generalization of those models, mainly in that here players do not suffer any cognitive constraint, and we allow for larger and possibly variable classes of games.}

A choice mechanism associates decision situations with action choices. A crucial part of a
choice mechanism is the \emph{subjective representation} of the decision situation, in
particular the manner of forming preferences and beliefs about a possibly uncertain world. To
show the usefulness of the meta-game approach, this paper asks: which preference and belief
representations are ecologically valuable and lead to high fitness? The evolution of
preferences has been subject of recent interest in theoretical economics
\citep[e.g.,][]{algweib13,DekElyYlan07,RobSam11}. Here, we argue that questions of preference
evolution should take variability in uncertainty representation into account as well. We
demonstrate that if agents have \emph{imprecise} probabilistic beliefs
\citep[e.g.,][]{gardsah82,levi74,walley96}, faithful and objective representations in terms of
true, real evolutionary fitness can be outperformed by subjective (e.g., regret-based)
preference representations that deviate from the true fitness that natural selection operates
on.

@@

The paper is organized as follows. Section \ref{sec:rati--subj} sets the scene by reviewing
different perspectives on rational choice. Section~\ref{sec:subj-ut,bel,dec-rules}
introduces the meta-game approach. In doing so, it covers key notions such as choice mechanisms,
decision rules and subjective representations, all with an eye towards the evolutionary applications
of Section~\ref{sec:model}. Section~\ref{sec:results} contains
the main results, and Section \ref{sec:extensions} discusses some
interesting extensions. Finally, Section~\ref{sec:conclusion} concludes.

@@

An alternative view on rationality of choice is \emph{adaptationism}
\citep[e.g.,][]{Anderson1991:Is-human-cognit,ChaterOaksford2000:The-Rational-An,HagenChater2012:Decision-Making}. Adaptationism
aims to explain rational behavior by appealing to evolutionary considerations: DMs have acquired
choice mechanisms that have proved to be adaptive with respect to the variable environment
where they have evolved. A choice mechanism can be a set of distinct heuristics (the DM's
\emph{adaptive toolbox}) that have little in common
\citep[e.g.,][]{TverskyKahnemann1981:The-Framing-of-,GigerenzerGoldstein1996:Reasoning-the-F,ScheibehenneRieskamp2013:Testing-the-Ada}. But
to closely relate to the literature on evolution of preferences and to the philosophical debate
about the nature of rational choice, we here suggest to think of a choice mechanism
as a map from choice situations to action choices which includes an explicit level of subjective representation of the situation. Specifically, a \emph{subjective representation} is a general way of forming preferences and beliefs about the choice situation, and we
are most interested in the question which subjective representations, and which choice mechanisms in general, are better than others
from an evolutionary point of view.

@@

We view a choice mechanism as the combination of three different things: a \textit{subjective utility} (or preference), a \textit{subjective belief} and a \textit{decision rule}. In general, the agent's action choice will depend both on the agent's utility at different possible outcomes of the choice situation and on the agent's beliefs about the realization of these outcomes. The decision rule then combines the agent's subjective utility and belief, and dictates how the agent should act in case of a choice situation whose consequences are uncertain. Therefore, a decision rule is a function that associates an action choice with the agent's utility and beliefs:
$$ \text{Decision Rule: Utility }\times\text{ Beliefs } \rightarrow \text{ Actions.}  $$
The subjective utility of an agent can be formally expressed by a function
$u:W \times A \rightarrow \mathbb{R} $, where $A$ stands for a (finite) set of actions
available to the agent and $W$ is a (finite) set of possible states of the world. There are
many different ways to describe beliefs, but for concreteness of later applications we here
assume that the agent's beliefs are represented in terms of a (possibly singleton) convex compact set of
probability functions $\Gamma \subseteq \Delta(W) $ over the possible states of the
world. Given a utility $u$ and a belief $\Gamma$, examples of well-known decision rules from the literature that we will encounter later are:
\begin{enumerate}

@@

It is worth noticing that both maxmin and maximax boil down to expected utility maximization
when the set $\Gamma$ is a singleton, and in turn expected utility maximization reduces to
Laplace rule when the belief $\mu$ is a uniform probability over the states.

As mentioned previously, for a choice mechanism to prescribe an action, the decision rule needs
to be given a specific utility $u$ and belief $\Gamma$ as input. We call the pair $(u,\Gamma)$ a \textit{subjective
  representation} of the decision problem. In the following, we investigate the evolutionary fitness of general and systematic ways of
forming such subjective representations across many different decision situations.

@@

However, studying the fitness and the evolutionary selection of different choice mechanisms by
the use of a fixed, single game may look like a rather restrictive perspective and possibly
biased by the choice of the particular game. To avoid these limitations, we consider a
\textit{class} of possible games. Towards this end, fix a class $\mathcal{G}$ of possible two-player symmetric games,
together with a probability measure $P_{\mathcal{G}}(G)$ for the occurrence probability of game
$G \in \mathcal{G}$. Intuitively, the probability $P_{\mathcal{G}}$ encodes the statistical
properties of the environment. A \textit{meta-game} is then a tuple
$ MG=\langle CM, \mathcal{G}, P_{\mathcal{G}},F \rangle$, where $CM$ is a set of choice
mechanisms, $\mathcal{G}$ is a class of possible games, $P_{\mathcal{G}}(G)$ is the probability
of game $G$ to occur, and $F:CM \times CM \rightarrow \mathbb{R}$ is the (meta-)fitness function,
defined as:
\begin{align}
  \label{eq:FittnessChoiceMechGamePairwise}
  F(c, c') = \int P_{\mathcal{G}}(G) \  F_G(c,c') \text{ d} G \,.
\end{align}
Hence, $F(c,c')$ determines the evolutionary payoff of choice mechanism $c$ against $c'$ in the
meta-game. The set $CM$ can be thought of as the set of choice mechanisms that are present within a given
population playing the games from the class $\mathcal{G}$. Consequently, it is possible
to compute the average fitness of $c$ against the population, that is given by:
\begin{align}
  \label{eq:FittnessChoiceMechGame}
  F(c) = \int P_{M}(c') \ F(c,c') \text{ d} c' = \int \int P_{\mathcal{G}}(G) \  P_{M}(c') \  F_G(c,c') \text{ d} c' \text{ d} G  \,,
\end{align}
where $P_{M}(c')$ is the probability of
encountering a co-player with choice mechanism $c'$.

@@

Although a thorough discussion of this issue goes beyond the scope of this work, let us say
that these two kinds of belief underlie two different and alternative views on
uncertainty. Faced with uncertain events, a strict Bayesian will always form a precise belief,
specified by a \textit{single} probability $\mu$. In the absence of any information about
future uncertain events, the Bayesian would mostly invoke the \textit{principle of insufficient
  reason}, and accordingly choose a uniform probability over the possible outcomes. In
contrast, others have argued against the obligation of representing a belief by means of a
single probability measure, opposite to the Bayesian paradigm (e.g., \cite{GilbMarin13}). They argue
instead in favor of a more encompassing account, according to which uncertainty can be \emph{unmeasurable},
and represented by a (convex and compact) set of probabilities (e.g., \cite{gilsch89}). This line of thought has been
originated in decision theory by the famous Ellsberg's paradoxes \citep{ells61}, and appears extremely
relevant in game-theoretic contexts too. Indeed, in a recent paper \citet{BattCerrMM15}
write:

@@

As for the decision rule, we assume that players use the maxmin rule. This is in line with many representation
results of decision making under unmeasurable uncertainty \citep[e.g.,][]{gilsch89,GhirMar02},
and seems corroborated by empirical findings too. Ellsberg's paradoxes are prominent examples (\citet{ells61}), and evidence from experimental literature suggests that agents are generally averse to unmeasurable uncertainty \citep[e.g.,][]{TrautKuil16}.

Finally, note that when the maxmin rule acts on subjective representation (obj, imp), the
generated behavior corresponds to the classic maxmin strategy \citep{neumorg44}. When the maxmin rule acts on
subjective representation (reg, imp), the agent's behavior is known as \textit{regret
  minimization}.\footnote{The notion of regret in decision theory dates back at least to the
  work by \citet{Savage1951:The-theory-of-s}, and has later been developed by \citet{bell82},
  \citet{Fishburn1982} and \citet{loosug82} independently. Recently,
  \citet{HalpernPass2012:Iterated-Regret} showed how the use of regret minimization can give
  solutions to game-theoretic puzzles (like the Traveller's dilemma and the Centipede game)
  in a way that is closer to everyday intuition and empirical data. In this paper the notion of
  regret defined earlier is the same as in \citet{HalpernPass2012:Iterated-Regret}.} Two facts
stem from these observations.  The first is related to our focus on different types of
uncertainty that players may entertain.
\begin{fact} \label{fact:maxEU-minReg} 
%Under an identical precise (singleton set) belief, the
%  acts selected by maximization of expected evolutionary payoff in game $G$ are exactly the acts selected
%  by the maximization of expected utility for the negative regret transformation of $G$
For any precise (Bayesian) and identical belief, maximization of expected (objective) utility and minimization of expected regret are behaviorally equivalent. %\citep[e.g.,][]{HalpernPass2012:Iterated-Regret}.
\end{fact}
\noindent The second fact highlights another behavioral equivalence, which we will make use of shortly in the following section.
\begin{fact} \label{fact:equivalence2x2} In the class of $2 \times 2$ symmetric games, the acts
  selected by Laplace rule are exactly the acts selected by regret minimization.
\end{fact}

@@

As observed earlier, meta-games factor in statistical properties of the environment. For particular
empirical purposes, one could consult a specific class of games $\mathcal{G}$ with appropriate,
maybe empirically informed probability $P_{\mathcal{G}}$ in order to match the natural
environment of a given population. For our theoretic purposes, let $\mathcal{G}$ be a set of symmetric
two-player fitness games with two acts for a start. Each game $G \in \mathcal{G}$ is then individuated solely by its payoff
function, i.e., by a quadruple of numbers $G=(a,b,c,d)$. As for the occurrence probability
$P_{\mathcal{G}}(G)$ of game $G$, we imagine that the values $a,b,c,d$ are i.i.d.~random
variables sampled from the set $ \lbrace 0, \dots, 10 \rbrace$ according to uniform probability
$P_{V}$. Using Monte Carlo simulations, we can then approximate the values of
equation~(\ref{eq:FittnessChoiceMechGamePairwise}) to construct meta-game payoffs. Results
based on $100.000$ randomly sampled games are given in
table~\ref{tab:ExpectedFitness_4Types}.\footnote{Concretely, $100.000$ games were sampled
  repeatedly by choosing independently four integers between 0 and 10 uniformly at random. For
  each game, the action choices of all four choice mechanisms were determined and payoffs from
  all pairwise encounters recorded. The number in each cell of
  table~\ref{tab:ExpectedFitness_4Types} is the average payoff for the choice mechanism listed
  in the row when matched with the choice mechanism in the column.}

@@

This result presupposes at least occasional imprecise beliefs. The assumed imprecise beliefs do not need to be maximally uncertain, however.  Let
the uncertainty held by a player be defined by a convex compact set of probabilities
$ [s,t] \subseteq \Delta(A) $ over the co-player's actions, where $s$ is the lower probability
and $t$ is the upper probability of action $II$.  We can then prove the following proposition,
which is the equivalent of Proposition~\ref{proposition1} for any possible (not necessarily
maximal) degree of uncertainty $[s,t]$, with $s \neq t$. There is only one difference: we are
now going to require i.i.d. drawing of a \emph{continuous} random variable. This is due to the
fact that, for arbitrarily small intervals $[s,t]$, objective players $([s,t],\text{obj})$ and
regret players $([s,t],\text{reg})$ can behave as holding a unique probability measure (precise
belief) if the underlying payoff space is not dense. The reason for this technical requirement
will become clearer from the proof.

@@

This tells us that regret-based preferences can outperform objective preference
representations when agents are also capable of learning or otherwise restrict their assumptions
about the co-player's behavior as long as there is, at least on occasion, some imprecision in
their beliefs. We will enlarge on the issue of belief formation after having covered some more
relevant extensions in the next section.

@@

Since one of our main purposes was to illustrate the usefulness of a meta-game approach
by the case study of objective and regret preferences, we have partially neglected an 
important and interesting issue, namely the evolution of ways of forming beliefs
about co-players' behavior or the actual state of the world. For reasons of space we must,
unfortunately, leave a deeper exploration of belief type evolution to another occasion. Two
remarks are in order nonetheless. Firstly, belief type evolution can be studied without
conceptual hurdles in the meta-game framework, so that there is no principled argument
against the main methodological contribution of this paper. Secondly, our results regarding the
comparison between regret and objective types remain to be informative, even if we
allow agents to learn or reason strategically.\footnote{Some research has recently been done along these lines. See in particular \cite{RobalinoRobson16,Mengel12,Mohlin12}.} This is because we know from
Fact~\ref{fact:maxEU-minReg} that regret and objective preferences come up behaviorally
equivalent when paired with precise probabilistic beliefs (given identical decision rule). This
holds no matter what the content of that belief is. So, if learning, reasoning or statistical
knowledge about a recurrent situation can be brought to bear, this will not make evolution
select against regret-based preferences. If, on the other hand, agents resort to imprecise
beliefs at least occasionally (e.g., when they are unaware of the co-player or her utilities,
or when strategic reasoning cannot reduce all uncertainty about the co-player's choice), then we
have shown that there are general and basic circumstances in which regret-based preferences
are favored by natural selection over objective preferences.

@@

The assumption that players and decision makers maximize their (subjective) utility is
central through all economic literature, and the maximization of actual (objective) payoffs is
often justified by appealing to evolutionary arguments and natural selection. In contrast to
the standard view, we showed the existence of player types with subjective utilities different
from the actual evolutionary payoffs that can outperform types whose subjective utilities
coincide with the evolutionary payoffs. Here the claim is not that regret preferences are the best on the market, but rather that utilities that perfectly mirror evolutionary fitness can be outclassed by subjective utilities that differ from the objective fitness.  While the literature on evolution of preferences has
focused on fixed games, we have adopted a more general approach here. We suggested that
attention to “meta-games” is crucial, because what may be a good subjective representation in
one type of game (e.g., cooperative preferences in the Prisoner’s Dilemma class) need not be
generally beneficial. Taken together, we presented a variety of plausible circumstances in
which evolutionary competition between choice mechanisms on a larger class of games can favor
non-veridical preference representations focusing on regret.

>>>>

If agents deal with a rich and variable environment, they have to face many different choice
situations.  Standard evolutionary game models frequently simplify reality in at least two
ways. Firstly, the environment is represented as a fixed \emph{stage game}; secondly, the focus
of evolutionary selection is behavior for that stage game alone. In contrast, some argue for
studying the evolutionary competition of general \emph{choice mechanisms} in a rich and
variable environment
\citep[e.g.,][]{FawcettHamblin2013:Exposing-the-be,McNamara2013:Towards-a-Riche,HammStev12}. In
response to this and adding to recent like-minded approaches, this paper introduces a general
\emph{meta-game} model that conservatively extends the scope of evolutionary game theory to
deal with evolutionary selection of choice mechanisms in variable environments \citep[see
also][]{Harley1981:Learning-the-Ev,ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o,OConnor2016:Evolving-to-Gen,RayoBecker07,Zollman2008,SkyrmsZollman10,BednarPage07}.\footnote{Some
  of these contributions are very closely related to ours. \citet{BednarPage07} use a
  multi-game framework, composed of a fixed selection of six possible games, to study the
  emergence of different cultural behaviors, and model agents as finite-state automata playing
  games from the fixed selection. \citet{Zollman2008} explains seemingly ``irrational'' fair
  behavior in social dilemmas (like the Ultimatum game) by means of a model where agents have
  to play the Ultimatum game together with the Nash bargaining game, but they are constrained
  to choose the same strategy for both games. Finally, \citet{RayoBecker07} consider, in a more
  decision-theoretic setting, what subjective utility function a cognitively limited agent
  should be endowed with in order to maximize her evolutionary fitness. Our framework can then
  be viewed as a generalization of those models, mainly in that here players do not necessarily
  have any specific cognitive limitations, and we allow for larger and possibly variable
  classes of games.}

A choice mechanism associates decision situations with action choices. A crucial part of a
choice mechanism is the \emph{subjective representation} of the decision situation, in
particular the manner of forming preferences and beliefs about a possibly uncertain world. To
show the usefulness of the meta-game approach, this paper asks: which preference and belief
representations are ecologically valuable and lead to high fitness? The evolution of
preferences has been subject of recent interest in theoretical economics
\citep[e.g.,][]{algweib13,DekElyYlan07,RobSam11}. Here, we argue that questions of preference
evolution should take variability in uncertainty representation into account as well. We
demonstrate that if agents have \emph{imprecise} probabilistic beliefs
\citep[e.g.,][]{gardsah82,levi74,walley96}, faithful and objective representations in terms of
true evolutionary fitness can be outperformed by subjective (e.g., regret-based)
preference representations that deviate from the true fitness that natural selection operates
on.

@@

The paper is organized as follows. Section \ref{sec:rati--subj} sets the scene by reviewing
different perspectives on rational choice. Section~\ref{sec:subj-ut,bel,dec-rules} introduces
the meta-game approach. In doing so, it covers key notions such as choice mechanisms, decision
rules and subjective representations, all with an eye towards the evolutionary application of
Section~\ref{sec:model}. Section~\ref{sec:results} contains the main results for that
application, and Section \ref{sec:extensions} discusses some interesting extensions. Finally,
Section~\ref{sec:conclusion} concludes.

@@

An alternative view on rationality of choice is \emph{adaptationism}
\citep[e.g.,][]{Anderson1991:Is-human-cognit,ChaterOaksford2000:The-Rational-An,HagenChater2012:Decision-Making}. Adaptationism
aims to explain rational behavior by appealing to evolutionary considerations: DMs have
acquired choice mechanisms that have proved to be adaptive with respect to the variable
environment where they have evolved. A choice mechanism can be a set of distinct heuristics
(the DM's \emph{adaptive toolbox}) that have little in common
\citep[e.g.,][]{TverskyKahnemann1981:The-Framing-of-,GigerenzerGoldstein1996:Reasoning-the-F,ScheibehenneRieskamp2013:Testing-the-Ada}. But
to closely relate to the literature on evolution of preferences and to the philosophical debate
about the nature of rational choice, we here suggest to think of a choice mechanism as a map
from choice situations to action choices which includes an explicit level of subjective
representation of the situation. Specifically, a \emph{subjective representation} is a general
way of forming preferences and beliefs about the choice situation. We are most interested in
the question which subjective representations, and which choice mechanisms in general, are
better than others from an evolutionary point of view.

@@

We view a choice mechanism as the combination of three different things: a \textit{subjective
  utility} (or preference), a \textit{subjective belief} and a \textit{decision rule}. In
general, the agent's action choice will depend both on the agent's utility at different
possible outcomes of the choice situation and on the agent's beliefs about the realization of
these outcomes. The decision rule then combines the agent's subjective utility and belief, and
dictates how the agent should act: a decision rule is a function that associates an action
choice with the agent's utility and beliefs:
$$ \text{Decision Rule: Utility }\times\text{ Beliefs } \rightarrow \text{ Actions.}  $$
The subjective utility of an agent can be formally expressed by a function
$u:W \times A \rightarrow \mathbb{R} $, where $A$ stands for a (finite) set of actions
available to the agent and $W$ is a (finite) set of possible states of the world. There are
many different ways to describe beliefs, but for concreteness of later applications we here
assume that the agent's beliefs are represented in terms of a (possibly singleton) convex compact set of
probability functions $\Gamma \subseteq \Delta(W) $ over the possible states of the
world. Given a utility $u$ and a belief $\Gamma$, examples of well-known decision rules from the literature that we will encounter later are:
\begin{enumerate}

@@

It is worth noticing that both maxmin and maximax boil down to expected utility maximization
when the set $\Gamma$ is a singleton, and in turn expected utility maximization reduces to the
Laplace rule when the belief $\mu$ is a uniform probability over the states.

As mentioned previously, for a choice mechanism to prescribe an action, the decision rule needs
to be given a specific utility $u$ and belief $\Gamma$ as input. We call the pair $(u,\Gamma)$
a \textit{subjective representation} of the decision situation. In the following, we investigate
the evolutionary fitness of general and systematic ways of forming such subjective
representations across many different decision situations.

@@

Going beyond a single fixed fitness game, we consider a \textit{class} of possible games. For
concreteness, let $\mathcal{G}$ be a class of two-player symmetric games, together with a
probability measure $P_{\mathcal{G}}(G)$ for the occurrence probability of game
$G \in \mathcal{G}$. Intuitively, the probability $P_{\mathcal{G}}$ encodes the statistical
properties of the environment. A \textit{meta-game} is then a tuple
$ MG=\langle CM, \mathcal{G}, P_{\mathcal{G}},F \rangle$, where $CM$ is a set of choice
mechanisms, $\mathcal{G}$ is a class of possible games, $P_{\mathcal{G}}(G)$ is the probability
of game $G$ to occur, and $F:CM \times CM \rightarrow \mathbb{R}$ is the (meta-)fitness
function, defined as:
\begin{align}
  \label{eq:FittnessChoiceMechGamePairwise}
  F(c, c') = \int P_{\mathcal{G}}(G) \  F_G(c,c') \text{ d} G \,.
\end{align}
Hence, $F(c,c')$ determines the evolutionary payoff of choice mechanism $c$ against $c'$ in the
meta-game. The set $CM$ can be thought of as the set of choice mechanisms that are present within a given
population playing the games from the class $\mathcal{G}$. Consequently, it is possible
to compute the average fitness of $c$ against the population, that is given by:
\begin{align}
  \label{eq:FittnessChoiceMechGame}
  F(c) = \int P_{M}(c') \ F(c,c') \text{ d} c' = \int \int P_{\mathcal{G}}(G) \  P_{M}(c') \  F_G(c,c') \text{ d} c' \text{ d} G  \,,
\end{align}
where $P_{M}(c')$ is the probability of
encountering a co-player with choice mechanism $c'$.

@@

Although a thorough discussion of this issue goes beyond the scope of this work, let us say
that these two kinds of belief underlie two different and alternative views on
uncertainty. Faced with uncertain events, a strict Bayesian will always form a precise belief,
specified by a \textit{single} probability $\mu$. In the absence of any information about
future uncertain events, the Bayesian would mostly invoke the \textit{principle of insufficient
  reason}, and accordingly choose a uniform probability over the possible outcomes. In
contrast, others have argued against the obligation of representing a belief by means of a
single probability measure, opposite to the Bayesian paradigm (e.g., \cite{GilbMarin13}). They
argue instead in favor of a more encompassing account, according to which uncertainty can be
\emph{unmeasurable}, and represented by a (convex and compact) set of probabilities (e.g.,
\cite{gilsch89}). This line of thought has its origin in decision theory, motivated by
Ellsberg's famous paradoxes \citep{ells61}, and appears extremely relevant in game-theoretic
contexts too. Indeed, in a recent paper \citet{BattCerrMM15} write:

@@

As for the decision rule, we assume that players use the maxmin rule. This is in line with many
representation results of decision making under unmeasurable uncertainty
\citep[e.g.,][]{gilsch89,GhirMar02}, and seems corroborated by empirical findings
too. Ellsberg's paradoxes are prominent examples \citep{ells61}, and evidence from experimental
literature suggests that agents are generally averse to unmeasurable uncertainty
\citep[e.g.,][]{TrautKuil16}.

Finally, note that when the maxmin rule acts on subjective representations of type (obj, imp),
i.e., objective preferences and imprecise beliefs, the generated behavior corresponds to the
classic maxmin strategy \citep{neumorg44}. When the maxmin rule acts on subjective
representation (reg, imp), the agent's behavior is known as \textit{regret
  minimization}.\footnote{The notion of regret in decision theory dates back at least to the
  work by \citet{Savage1951:The-theory-of-s}, and has later been developed by \citet{bell82},
  \citet{Fishburn1982} and \citet{loosug82} independently. Recently,
  \citet{HalpernPass2012:Iterated-Regret} showed how the use of regret minimization can give
  solutions to game-theoretic puzzles (like the Traveller's dilemma and the Centipede game) in
  a way that is closer to everyday intuition and empirical data. In this paper the notion of
  regret defined earlier is the same as in \citet{HalpernPass2012:Iterated-Regret}.} Two facts
follow from these observations.  The first is related to our focus on different types of
uncertainty that players may entertain.
\begin{fact} \label{fact:maxEU-minReg} 
%Under an identical precise (singleton set) belief, the
%  acts selected by maximization of expected evolutionary payoff in game $G$ are exactly the acts selected
%  by the maximization of expected utility for the negative regret transformation of $G$
  For any precise (Bayesian) belief $\mu$, maximization of expected (objective) utility based
  on $\mu$ and minimization of expected regret based on $\mu$ are behaviorally
  equivalent. %\citep[e.g.,][]{HalpernPass2012:Iterated-Regret}.
\end{fact}
\noindent The second fact highlights another behavioral equivalence, which we will make use of
shortly in the following section.
\begin{fact} \label{fact:equivalence2x2} In the class of $2 \times 2$ symmetric games, the acts
  selected by the Laplace rule are exactly the acts selected by regret minimization.
\end{fact}

@@

As observed earlier, meta-games factor in statistical properties of the environment. For particular
empirical purposes, one could consult a specific class of games $\mathcal{G}$ with appropriate,
maybe empirically informed probability $P_{\mathcal{G}}$ in order to match the natural
environment of a given population. For our present purposes, let $\mathcal{G}$ be a set of symmetric
two-player fitness games with two acts for a start. Each game $G \in \mathcal{G}$ is then individuated solely by its payoff
function, i.e., by a quadruple of numbers $G=(a,b,c,d)$. As for the occurrence probability
$P_{\mathcal{G}}(G)$ of game $G$, we imagine that the values $a,b,c,d$ are i.i.d.~random
variables sampled from the set $ \lbrace 0, \dots, 10 \rbrace$ according to uniform probability
$P_{V}$. Using Monte Carlo simulations, we can then approximate the values of
equation~(\ref{eq:FittnessChoiceMechGamePairwise}) to construct meta-game payoffs. Results
based on $100.000$ randomly sampled games are given in
table~\ref{tab:ExpectedFitness_4Types}.\footnote{Concretely, $100.000$ games were sampled
  repeatedly by choosing independently four integers between 0 and 10 uniformly at random. For
  each game, the action choices of all four choice mechanisms were determined and payoffs from
  all pairwise encounters recorded. The number in each cell of
  table~\ref{tab:ExpectedFitness_4Types} is the average payoff for the choice mechanism listed
  in the row when matched with the choice mechanism in the column.}

@@

This result presupposes at least occasional imprecise beliefs. The assumed imprecise beliefs do not need to be maximally uncertain, however.  Let
the uncertainty held by a player be defined by a convex compact set of probabilities
$ [s,t] \subseteq \Delta(A) $ over the co-player's actions, where $s$ is the lower probability
and $t$ is the upper probability of action $II$.  We can then prove the following proposition,
which is the analogue of Proposition~\ref{proposition1} for any possible (not necessarily
maximal) degree of uncertainty $[s,t]$, with $s \neq t$. There is only one difference: we are
now going to require i.i.d. drawing of a \emph{continuous} random variable. This is due to the
fact that, for arbitrarily small intervals $[s,t]$, objective players $([s,t],\text{obj})$ and
regret players $([s,t],\text{reg})$ can behave as holding a unique probability measure (precise
belief) if the underlying payoff space is not dense. The reason for this technical requirement
will become clearer from the proof.

@@

This tells us that regret-based preferences can outperform objective preference
representations when agents are also capable of learning or otherwise restricting their assumptions
about the co-player's behavior as long as there is, at least on occasion, some imprecision in
their beliefs. We will enlarge on the issue of belief formation after having covered some more
relevant extensions in the next section.

@@

Since one of our main purposes was to illustrate the usefulness of a meta-game approach by the
case study of objective and regret preferences, we have partially neglected an important and
interesting issue, namely the evolution of ways of forming beliefs about co-players' behavior
or the actual state of the world. For reasons of space we must, unfortunately, leave a deeper
exploration of belief type evolution to another occasion. Two remarks are in order
nonetheless. Firstly, belief type evolution can be studied without conceptual hurdles in the
meta-game framework, so that there is no principled argument against the main methodological
contribution of this paper. Secondly, our results regarding the comparison between regret and
objective types remain to be informative, even if we allow agents to learn or reason
strategically.\footnote{Some research has recently been done along these lines. See in
  particular \cite{RobalinoRobson16,Mengel12,Mohlin12}.} This is because we know from
Fact~\ref{fact:maxEU-minReg} that regret and objective preferences come up behaviorally
equivalent when paired with precise probabilistic beliefs (given identical decision rule). This
holds no matter what the content of that belief is. So, if learning, reasoning or statistical
knowledge about a recurrent situation can be brought to bear, this will not make evolution
select against regret-based preferences. If, on the other hand, agents resort to imprecise
beliefs at least occasionally (e.g., when they are unaware of the co-player or her utilities,
or when strategic reasoning cannot reduce all uncertainty about the co-player's choice), then
regret-based preferences can be favored by natural selection over objective preferences.

@@

The assumption that players and decision makers maximize their (subjective) utility is central
through in the economics literature, and the maximization of actual (objective) payoffs is
often justified by appealing to evolutionary arguments and natural selection. In contrast to
the standard view, we showed the existence of player types with subjective utilities different
from the actual evolutionary payoffs that can outperform types whose subjective utilities
coincide with the evolutionary payoffs. The claim is not that regret preferences are the best
on the market, but rather that utilities that perfectly mirror evolutionary fitness can be
outclassed by subjective utilities that differ from the objective fitness.  While the
literature on evolution of preferences has focused on fixed games, we have adopted a more
general approach here. We suggested that attention to “meta-games” is crucial, because what may
be a good subjective representation in one type of game (e.g., cooperative preferences in the
Prisoner’s Dilemma class) need not be generally beneficial. Taken together, we presented a
variety of plausible circumstances in which evolutionary competition between choice mechanisms
on a larger class of games can favor non-veridical preference representations focusing on
regret.
